Look, we can do something

### 2024-11-08 paper.tex
Small improvement
Fix elongation definition

In this paper we also use the following common parameters which are used to
describe pore shapes:
\begin{itemize}
\item Convexity $C$ is a relation between surface of a pore and surface bounded
  by its convex hull.
\item Roundness $R$ is a relation between perimeter of a disk which has the same
  surface as a pore to perimeter of that pore.
\item Elongation $E$ is a relation between eigenvalues of a matrix $A$ with the
  smallest and the biggest absolute values. $A$ is a $2 \times 2$ covariation
  matrix of coordinates of pore points. For a discrete image of a pore its
  elements equal to
  \begin{equation*}
    a_{ij} = \sum_{x \in \left\{
      \begin{array}{l}
        \text{Coordinates of points} \\
        \text{belonging to the pore}
      \end{array}
      \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
  \end{equation*}
\end{itemize}
All of these parameters lie in the range $[0, 1]$.

@@

\section{Summary}
In this paper we have developed a new parameter for assession of pore
clusterization quality which can be used as a replacement for roundness
parameter. Benefits of this parameter include:
\begin{itemize}
\item Lower absoulute value of correlation with other common parameters, such as
  convexity, elongation and roundness.
\item Ease of computation.
\item Ability to precisely separate well-clusterized pores and underclusterized
  pores in a high convexity range, even if roundness fails to do so.
\item Rotation and resize invariance.
\end{itemize}

>>>>

In this paper we also use the following common parameters which are used to
describe pore shapes:
\begin{itemize}
\item Convexity $C$ is a relation between surface of a pore and surface bounded
  by its convex hull.
\item Roundness $R$ is a relation between perimeter of a disk which has the same
  surface as a pore to perimeter of that pore.
\item Elongation $E$ is a square root of a relation
  $|\frac{\lambda_1}{\lambda_2}|$ where $\lambda_1$ and $\lambda_2$ are two
  eigenvalues of a matrix $A$ which is a $2 \times 2$ covariation matrix of
  coordinates of pore points. For a discrete image of a pore its elements equal
  to
  \begin{equation*}
    a_{ij} = \sum_{x \in \left\{
      \begin{array}{l}
        \text{Coordinates of points} \\
        \text{belonging to the pore}
      \end{array}
      \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
  \end{equation*}
  Eigenvalues are enumerated so that $E$ is no bigger than $1$.
\end{itemize}
All of these parameters lie in the range $[0, 1]$.

@@

\section{Summary}
In this paper we have developed a new parameter for assession of pore
clusterization quality which can be used as a replacement for roundness
parameter. Benefits of this parameter include:
\begin{itemize}
\item Lower absoulute value of correlation with other common parameters, such as
  convexity, elongation and roundness.
\item Ease of computation and interpretation.
\item Ability to precisely separate well-clusterized pores and underclusterized
  pores in a high convexity range, even if roundness fails to do so.
\item Rotation and resize invariance.
\end{itemize}
